---
title: "group project 2"
author: "Group 05"
date: "2022/3/15"

output:
  pdf_document:
    toc: yes

output: 
  pdf_document:
    toc: yes
  

  html_document:
    df_print: paged
    toc: yes
    theme: united
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(dplyr)
library(tidyverse)
library(moderndive)
library(gapminder)
library(sjPlot)
library(stats)
library(jtools)
library(MASS)
library(BMA)
library(ROCR)
library(GGally)
library(generalhoslem)

```

```{r}
film <- read.csv("dataset5.csv")
```
# Introduction of dataset
## Question to be explored
Imagine you have been asked by a film producer to investigate the following question of interest:

* Which properties of films influence whether they are rated by IMDB as greater than 7 or not?

You should conduct an analysis to answer your question using a Generalised Linear Model (GLM). <br>
Following your analyses, you should then summarise your results in the form of a presentation.

## Explain each variables
* film.id – The unique identifier for the film
* year – Year of release of the film in cinemas
* length – Duration (in minutes)
* budget – Budget for the films production (in $1000000s)
* votes – Number of positive votes received by viewers
* genre – Genre of the film
* rating – IMDB rating from 0-10

# Data processing
Create a column to separate the rating: >7(1), <=7(0)
```{r}
library(janitor)
```

# Introduction of dataset

## Question to be explored

Imagine you have been asked by a film producer to investigate the following question of interest:

-   Which properties of films influence whether they are rated by IMDB as greater than 7 or not?

You should conduct an analysis to answer your question using a Generalised Linear Model (GLM). <br> Following your analyses, you should then summarise your results in the form of a presentation.

## Explain each variables

-   film.id -- The unique identifier for the film
-   year -- Year of release of the film in cinemas
-   length -- Duration (in minutes)
-   budget -- Budget for the films production (in \$1000000s)
-   votes -- Number of positive votes received by viewers
-   genre -- Genre of the film
-   rating -- IMDB rating from 0-10

# Data processing

```{r}
film <- read.csv("dataset5.csv")
```

Create a column to separate the rating: \>7(1), \<=7(0)


```{r}
film <- film %>%
  mutate(rating.large7 = cut(rating, breaks = c(0,7,Inf), labels=c(0,1))) %>%
  dplyr::select(-film_id, -rating)%>%
  na.omit()
```



# Exploratory data analysis
## The distribution of rating.large7 by genre

# Exploratory data analysis

## The distribution of rating.large7 by genre


```{r}
film %>%
  group_by(genre, rating.large7)%>%
  summarise(n = n())
```

```{r}
plot_xtab(film$rating.large7,film$genre,show.values =FALSE,show.total =FALSE,
axis.labels =c("0","1"),
axis.titles=c("rating larger than 7?"))
```

## The distribution of rating.large7 by other numerical variables

```{r}
film %>% 
  tabyl(rating.large7, genre) %>% 
  adorn_percentages() %>% 
  adorn_pct_formatting() %>% 
  adorn_ns() 
```

## The distribution of rating.large7 by other numerical variables


```{r}
## budget
film.plot1<-ggplot(film, aes(y=budget,x=rating.large7))

film.plot1+geom_boxplot()+xlab("rating larger than 7?")+
theme(panel.background =element_rect(fill ="transparent",colour =NA),
plot.background =element_rect(fill ="transparent",colour =NA),
panel.border =element_rect(fill =NA,colour ="black",size =1))

## year
film.plot2<-ggplot(film, aes(y=year,x=rating.large7))

film.plot2+geom_boxplot()+xlab("rating larger than 7?")+
theme(panel.background =element_rect(fill ="transparent",colour =NA),
plot.background =element_rect(fill ="transparent",colour =NA),
panel.border =element_rect(fill =NA,colour ="black",size =1))

## votes
film.plot3<-ggplot(film, aes(y=log(votes),x=rating.large7))

film.plot3+geom_boxplot()+xlab("rating larger than 7?")+
theme(panel.background =element_rect(fill ="transparent",colour =NA),
plot.background =element_rect(fill ="transparent",colour =NA),
panel.border =element_rect(fill =NA,colour ="black",size =1))

## length
film.plot4<-ggplot(film, aes(y=length,x=rating.large7))

film.plot4+geom_boxplot()+xlab("rating larger than 7?")+
theme(panel.background =element_rect(fill ="transparent",colour =NA),
plot.background =element_rect(fill ="transparent",colour =NA),
panel.border =element_rect(fill =NA,colour ="black",size =1))
```





# Formal data analysis
## Take log transformation of variable "vote" because the scale is not linear.

# Formal data analysis

## Take log transformation of variable "vote" because the scale is not linear.


```{r}
film <- film %>%
  mutate(log.votes = log(votes))
```


## Stepwise Slection: choosing which variables need to be removed. 
Since Model with "year" removed has lowest AIC=1303.21 and deviance D=1283.2 we will go ahead and compared the three link function in our model

## Stepwise Slection: choosing which variables need to be removed.

Since Model with "year" removed has lowest AIC=1303.21 and deviance D=1283.2 we will go ahead and compared the three link function in our model


```{r}
model_sat <-  glm(rating.large7 ~ length + budget + genre + log.votes + year, family = binomial(link = "logit"), data = film)

logit.step <- step(model_sat,direction='both')
summary(logit.step)
```

## Comparing different link functions

The AIC and BIC in model1 is the smallest, and the Pseudo-R² is the largest. Hence we choose 'logit' link function to fit our model

### Model 1: logit link


The AIC and BIC in model1 is the smallest, and the Pseudo-R² is the largest. Hence we choose 'logit' link function to fit our model

### Model 1: logit link


```{r}
model1 <- glm(rating.large7 ~ length + budget + log.votes + genre, family = binomial(link = "logit"), data = film)
summary(model1)
```

```{r,eval=FALSE}
summ(model1)
```

### Model 2: probit link


```{r, echo=FALSE}
s1 <- summ(model1)
```

### Model 2: probit link


```{r}
model2 <- glm(rating.large7 ~ length + budget + log.votes + genre, family = binomial(link = "probit"), data = film)
summary(model2)
```

```{r,eval=FALSE}
summ(model2)
```

### Model 3: complementary log-log link


```{r, echo=FALSE}
s2 <- summ(model2)
```

### Model 3: complementary log-log link


```{r}
model3 <- glm(rating.large7 ~ length + budget + log.votes + genre, family = binomial(link = "cloglog"), data = film)
summary(model3)
```

```{r, eval=FALSE}
summ(model3)
```


## Residual Deviance
$$D_0-D_1 = 2982.5-1283.2 = 1699.3 >  {\chi}^2(0.95, 9) = 16.91898 $$ 


```{r, echo=FALSE}
s3 <- summ(model3)
```

| Model  | link function                                           |                         AIC |                         BIC |
|:-------|:--------------------------------------------------------|----------------------------:|----------------------------:|
| model1 | $g(p_i)=log(\frac{p_i}{1-p_i})$                         | `r round(attr(s1,"aic"),2)` | `r round(attr(s1,"bic"),2)` |
| model2 | $g(p_i)=\phi^{-1}(pi),p_i=\phi(\frac{x_i-\mu}{\sigma})$ | `r round(attr(s2,"aic"),2)` | `r round(attr(s2,"bic"),2)` |
| model3 | $g(p_i)=log[-log(1-p_i)]$                               | `r round(attr(s3,"aic"),2)` | `r round(attr(s3,"bic"),2)` |

## final model

$$log(\frac{p_{(rating.large7=1)}}{1-p_{(rating.large7=1)}}) = `r round(s1$model$coefficients[1],2)`+`r round(s1$model$coefficients[2],2)`length_i + `r round(s1$model$coefficients[3],2)`*budget_i + `r round(s1$model$coefficients[4],2)`*log(votes_i) + `r round(s1$model$coefficients[5],2)`*I_(genre=Animation) + `r round(s1$model$coefficients[6],2)`*I_(genre=Comedy) + `r round(s1$model$coefficients[7],2)`*I_(genre=Documentary) + `r round(s1$model$coefficients[7],2)`*I_(genre=Drama) + `r round(s1$model$coefficients[7],2)`*I_(genre=Romance) + `r round(s1$model$coefficients[7],2)`*I_(genre=Short)$$

$$I_{(genre=Animation)} = \begin{cases}
1, genre=Animation\\
0, otherwise
\end{cases},$$
$$I_{(genre=Comedy)} = \begin{cases}
1, genre=Comedy\\
0, otherwise
\end{cases},$$
$$I_{(genre=Documentary)} = \begin{cases}
1, genre=Documentary\\
0, otherwise
\end{cases},$$
$$I_{(genre=Drama)} = \begin{cases}
1, genre=Drama\\
0, otherwise
\end{cases},$$
$$I_{(genre=Romance)} = \begin{cases}
1, genre=Romance\\
0, otherwise
\end{cases},$$
$$I_{(genre=Short)} = \begin{cases}
1, genre=Short\\
0, otherwise
\end{cases}.$$



## Residual Deviance

$$D_0-D_1 = `r round(s1$model$null.deviance, 2)`-`r round(s1$model$deviance, 2)` = `r round(s1$model$null.deviance-s1$model$deviance, 2)` >  {\chi}^2(0.95, 9) = `r qchisq(0.95,9)` $$


We reject H0, and we can say that the model1 fits the data better than Null model.

```{r}
model1$null.deviance - model1$deviance
df = model1$df.null - model1$df.residual
qchisq(p=0.95, df = df)
```

## Deviance 
To assess the adequacy of the model1 compared to the full/saturated model 

The deviance of model1 is $D=1283.2> {\chi}^2(0.95,2)=5.991465$


## Deviance

To assess the adequacy of the model1 compared to the full/saturated model

The deviance of model1 is $D=`r round(s1$model$deviance, 2)`> {\chi}^2(0.95,2)=`r qchisq(0.95,2)`$


So we can conclude that there is no evidence of lack of fit for the model1.

```{r}
qchisq(p=0.95,df=(length(model_sat$coefficients)-length(model1$coefficients)))
```

## Odds ratios of model1


We interpret the odds ratios as follows: 
for the increase in the film’s length, the odds of rating bigger than 7 decrease;
for the increase in the film's budget, the odds of rating bigger than 7 increase;
for the increase in the film's votes, the odds of rating bigger than 7 increase;
Animation’s odds of survival were 0.71 times those of Action, Comedy’s odds of survival were 14.55 times those of Action, Documentary’s odds of survival were 135.39 times those of Action, Drama’s odds of survival were 0.12 times those of Action,
Short’s odds of survival were 66.17 times those of Action.

```{r}
plot_model(model1,show.values=TRUE)+
  scale_y_log10(limits = c(0.001, 1000))
```

# Prediction

```{r}
plot_model(model1,type="pred",terms=c("length"),axis.title=c("length","Prob(rating above 7)"))
plot_model(model1,type="pred",terms=c("log.votes"),axis.title=c("log.votes","Prob(rating above 7)"))
plot_model(model1,type="pred",terms=c("budget"),axis.title=c("budget","Prob(rating above 7)"))
plot_model(model1,type="pred",terms=c("genre"),axis.title=c("genre","Prob(rating above 7)"))
```

# Model checking and diagnostics

## ROC curve and AUC
```{r}
film$Prid <- predict(model1, film, type="response")
score <- prediction(film$Prid,film$rating.large7)
perf <- performance(score,"tpr","fpr")
auc <- performance(score,"auc")
perfd <- data.frame(x= perf@x.values[1][[1]], y=perf@y.values[1][[1]])
p4<- ggplot(perfd, aes(x= x, y=y)) + geom_line() +
xlab("False positive rate") + ylab("True positive rate") +
ggtitle(paste("Area under the curve:", round(auc@y.values[[1]], 3)))
p4
```


The area under Curve (AUC) = 0.948 indicated that model 1 is very good at predicting the films rating greater than 7 given all predictor variables. 

## Hosmer-Lemeshow goodness of fit test

The area under Curve (AUC) = 0.948 indicated that model 1 is very good at predicting the films rating greater than 7 given all predictor variables.

## Hosmer-Lemeshow goodness of fit test


$H_0:$ Model1 fits the data well

$H_1:$ Model1 is not a good fit for the data

```{r}
source(url("http://www.chrisbilder.com/categorical/Chapter5/AllGOFTests.R"))
HLTest(model1,g=6)
```


The large p-value = 0.2417 indicates no lack of fit for the model1 and we fail to reject $H_0$.
