---
title: "group project 2"
author: "karen"
date: "2022/3/15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(tidyverse)
library(moderndive)
library(gapminder)
library(sjPlot)
library(stats)
library(jtools)
library("MASS")
library(BMA)
library(ROCR)
```

```{r}
film <- read.csv("dataset5.csv")
```
# Introduction of dataset
## question of dataset
Imagine you have been asked by a film producer to investigate the following question of interest:
• Which properties of films influence whether they are rated by IMDB as greater than 7 or not?
You should conduct an analysis to answer your question using a Generalised Linear Model (GLM). 
Following your analyses, you should then summarise your results in the form of a presentation.
## explain each variables
• film.id – The unique identifier for the film
• year – Year of release of the film in cinemas
• length – Duration (in minutes)
• budget – Budget for the films production (in $1000000s)
• votes – Number of positive votes received by viewers
• genre – Genre of the film
• rating – IMDB rating from 0-10

# create a col seperate the rate: >7, <=7
```{r}
film <- film %>%
  mutate(rating.large7 = cut(rating, breaks = c(0,7,Inf), labels=c(0,1)))
```

```{r}
model <-  glm(rating.large7 ~ year + length + budget + votes , family = binomial(link = "cloglog"), data = film)

logit.step <- step(model,direction='both')
summary(logit.step)
```
```{r}
model1 <- glm(rating.large7 ~ length + budget + votes + genre, family = binomial(link = "cloglog"), data = film)
summ(model1)
```
```{r}
BIC.model <- bic.glm(x = data.frame(film[,2:6]), y=film$rating.large7,
                     f = rating.large7 ~ year + length + budget + votes + genre,
                     strict = FALSE, glm.family="binomial", factor.type=TRUE)
```

ROC
```{r}
titanic$Prid <- predict(mod.titan, titanic, type="response")
score <- prediction(titanic$Prid,titanic$survived)
perf <- performance(score,"tpr","fpr")
auc <- performance(score,"auc")
perfd <- data.frame(x= perf@x.values[1][[1]], y=perf@y.values[1][[1]])
p4<- ggplot(perfd, aes(x= x, y=y)) + geom_line() +
xlab("False positive rate") + ylab("True positive rate") +
ggtitle(paste("Area under the curve:", round(auc@y.values[[1]], 3)))
```

